\documentclass[sigconf]{acmart}
%\usepackage{times}

% do not change these values
%\baselineskip 12pt
%\textheight 10in
\textheight 638pt
%\textwidth 6.9in
%\oddsidemargin -0.3in
%\topmargin -0.3in
%\headheight 0in
%\headsep 0in

%\usepackage[utf8]{inputenc}
%\usepackage[english]{babel}
%\setcopyright{licensedcagov}
%\setcopyright{cagovmixed}
%\setcopyright{licensedothergov}

% DOI
%\acmDOI{10.475/123_4}

% ISBN
%\acmISBN{123-4567-24-567/08/06}

%Conference
%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
%  Paso, Texas USA}
%\acmYear{1997}
%\copyrightyear{2016}

%\acmPrice{15.00}


\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{amsmath}
\usepackage{amsopn}
\usepackage{comment}
\usepackage[ruled,linesnumbered,noend]{algorithm2e}
\usepackage{multirow}
\usepackage{enumitem}

\begin{document}

\newcommand{\Paragraph}[1]{\smallskip{\bf #1.}}
\newcommand{\Paragraphnopunc}[1]{\smallskip\noindent{\bf #1}}
\newcommand{\Paragraphwithindent}[1]{\smallskip{\bf #1.}}
\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}
\newcommand{\argmin}{\text{arg}\,\text{min}}
\newcommand{\argmax}{\text{arg}\,\text{max}}

%\theoremstyle{definition}
%\newtheorem{definition}{Definition}
\newtheorem{prop}{Proposition}
%\newtheorem{lemma}{Lemma}
%\newtheorem{theorem}{Theorem}


\title{LayerLSH: Rebuilding Locality-Sensitive Hashing Indices by Exploring Density of Hash Values}



\begin{abstract}
Locality-sensitive hashing (LSH) has attracted extensive research efforts for approximate nearest neighbors (NN) search. Many of these LSH-based index structures fail to take data distribution into account. They perform well in a uniform data distribution setting but exhibit unstable performance when the data are skewed. In this paper, we observe that the skewness of hash values resulted from skewed data is a potential reason for performance degradation. To address this problem, we propose to rebuild LSH indices by exploring the density of hash values. The hash values in dense/sparse ranges are carefully reorganized using a multi-layered structure, so that more efforts are put into indexing the dense hash values. We rebuild three representative LSH indices for illustration, the table-based structure E2LSH, the tree-based structure LSB, and the recently proposed data sensitive hashing DSH. Extensive experiments are conducted to show the effectiveness and efficiency of the reconstructed LSH indices.
\end{abstract}

%\keywords{LSH, approximate query, nearest neighbors}


\maketitle


\input{intro}
\input{pre}
\input{layerlsh}
%\input{layerlsb}
\input{extension}
%\input{distributed}
\input{expr}
\input{related}
\input{conclusion}


\bibliographystyle{abbrv}
\bibliography{./references}

%\input{Appendix}

\end{document}


